Examination of shapes! (homework exam)

### 2016-02-26 geometricAlgorithms/homeworkExam/homeworkExam.tex
some stuff about speed??
homwork exam finished 2 mostly...

After the border is found we pass it 
\section{Red and blue lines}
\begin{algorithmic}[1]
	\State
	$P_{ends} \gets R \cup B$ (flat) Mapped to endpoints where each segment
	produces two end points, the endpoints contain a reference to eachother
	and they aslo contain which color they are.
	\State
	$P_{sorted} \gets P_{ends}$ sorted on Y coordinate.
	\ForAll{$p_{current} \gets Next(P_{sorted})$}
	\EndFor
\end{algorithmic}

@@

\section{Polygon cut}
\section{Diagonal polygon cut}
\end{document}

>>>>

After the border is found we pass it to the FindXYSilhouette function.
This funtion will take at most $O(N)$ time, because the function
istelf will always try to stay at much on the border as possible with help
of the least rotating edge function. This function traverses all connecting
edges. This sounds like a loop in a loop but it isn't really, because the
first loop doesn't consider all elements (only the outer ring) and the second
loop considers the connection in the outer rings. So some elements may be
considered dubble but this is just one element (the least rotating edge).
Its also worth noting that the ``inside'' edges may never be considered by
either of these functions because they try to stay on the outside.
\section{Red and blue lines}
\begin{algorithmic}[1]
	\State
	$P_{ends} \gets R \cup B$ (flat) Mapped to endpoints where each segment
	produces two end points, the endpoints contain a reference to eachother
	and they aslo contain which color they are and are also marked
	valid.
	\State
	$P_{sorted} \gets P_{ends}$ sorted on Y coordinate.
	\State
	$S_{tatus} \gets $ empty binary tree that sorts on X axis
	$S_{result} \gets $ empty list
	\ForAll{$p_{current} \gets Next(P_{sorted})$}
		\If{$p_{current}$ is a start point of a blue line}
			Insert $p_{current}$ into $S_{tatus}$
		\State
		\ElsIf{$p_{current}$ is a start point of a red line}
			\State
			$t_{neigbours} \gets $ Insert $p_{current}$ into
			$S_{tatus}$ which returns the left and right neigbours
			in a tupple
			\If{$t_{neigbours}$ are not both blue lines}
				\State
				$p_{current}$ gets marked invalid.
			\EndIf
		\State
		\ElsIf{$p_{current}$ is an end point of a blue line}
			\State
			$t_{neigbours} \gets $ Insert $p_{current}$ into
			$S_{tatus}$ which returns the left and right neigbours
			in a tupple
			\If{$t_{neigbours}$ a red line}
				\State
				mark that line invalid if $t_{neigbours}$ does
				not contain a blue line.
			\EndIf
			\State
			Remove $p_{current}$ and its twin (so the start point) from$S_{tatus}$
		\State
		\ElsIf{$p_{current}$ is an end point of a red line}
			\State
			$t_{neigbours} \gets $ Insert $p_{current}$ into
			$S_{tatus}$ which returns the left and right neigbours
			in a tupple
			\If{both $t_{neigbours}$ are blue and the twin of $p_{current}$ was still marked valid}
				Add $p_{current}$ to $S_{result}$
			\EndIf
			\State
			Remove $p_{current}$ and its twin (so the start point) from$S_{tatus}$
		\EndIf
	\EndFor
\end{algorithmic}

@@

The events are the beginning of either a red or blue line and the ending of
a red or blue line.

If the beginning of a blue line is encoutnered it gets inserted into the
status structure.

If the beginning of a red line is encountered it gets also
inserted into the status structure, Once inserted we check if the line left
and right are blue lines, if not we mark it invalid.

If the ending of a blue line is encoured we check its neighbours. If either
of them are red we make sure the other neigbor is blue, if not we mark the red line as invalid.
Then we remove the blue line from the status structure.

If the ending of a red line is encounred we check if its invalid,
if so we remove it from the structure and continue.
If its not invalid we insert the ending into the status structure.
If this ending is has a blue two blue lines as neigbors we add it
to the result set.
Finally we remove it and continue.
\section{Polygon cut}
\section{Diagonal polygon cut}
\end{document}
